A Motion Blur Resilient Fiducial For Quadcopter Imaging

### 2014-12-02 WACV/paper.tex
Merging Prof. Sharat's changes

\author{Meghshyam G. Prasad\\
Dept. of Computer Science, IIT Bombay\\
{\tt\small meghshyam@cse.iitb.ac.in}
\and
Sharat Chandran\\
Dept. of Computer Science, IIT Bombay\\
{\tt\small sharat@cse.iitb.ac.in}
\and
Michael S. Brown\\
School of Computing, NUS\\
{\tt\small brown@comp.nus.edu.sg}
}
\maketitle

@@

In another setup we arranged our fiducials on four sides of a box and
revolved the quadcopter around the box (See video uploaded at \cite{video}).
Later, we repeated the process by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
frames from this sequence as well as the performance of both
fiducials. The overall detection rate of our tags is 90\% while that
of ARTags is only around 60\%.

>>>>

\author{Meghshyam G. Prasad  \&  Sharat Chandran\\
Dept. of Computer Science and Engineering, IIT Bombay\\
{\tt\small \{meghshyam,sharat\}@cse.iitb.ac.in}
% \and
% Sharat Chandran\\
% Dept. of Computer Science, IIT Bombay\\
% {\tt\small sharat@cse.iitb.ac.in}
\and
Michael S. Brown\\
School of Computing, NUS\\
{\tt\small brown@comp.nus.edu.sg}
}
\maketitle

@@

In another setup we arranged our fiducials on four sides of a box and
revolved the quadcopter around the box (See  \cite{video}).
Later, we repeated the process by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
frames from this sequence as well as the performance of both
fiducials. The overall detection rate of our tags is 90\% while that
of ARTags is only around 60\%.
